A self-consistency check for unitary propagation of Hawking quanta

### 2016-07-27 Draft_BH_shells.tex
typo label fixed

\begin{abstract}
The black hole information paradox presumes that local quantum field theory can provide unitary propagations from near-horizon modes to asymptotic Hawking quanta. 
Instead of invoking unknown quantum-gravity effects to modify such assumption, we propose a self-consistency check.
We re-examine this assumption by establishing an analogy to Feynman's analysis of a double-slit experiment. 
Feynman showed that the assumption of subsystem unitarity in double-slit experiment, namely ignoring the entanglement with the double-slit, becomes arbitrarily reliable when the screen to project the interference pattern goes to infinitely far away.
Analogously, here we ask whether a unitary propagation of Hawking quanta, namely ignoring the entanglement with the geometry, also becomes arbitrarily reliable in the limit of a large black hole. 
We present strong evidence that the result is negative, and we discuss how this is related to the information transfer from near-horizon geometry and the soft-hair proposal.
\end{abstract}

@@

This conflict has inspired many different proposals to modify one of the above three statements. 
For example, information loss or remnant \cite{Bek94} {\bf (XXX anyone knows a better reference for remnants?)} modifies the first statement; 
firewall \cite{BraPir09,AMPS} or ER=EPR \cite{MalSus13} modifies the second statement;
various proposals of nonlocal effects near the horizon \cite{Gid12,DodSil15,OsuPag16} or causal patch complementarity \cite{HuiYan13,IlgYan13,LowTho14}
\footnote{Independent of the particular realization, causal-patch complementarity basically claims that QFT breaks down if one applies it to a region that does not fit into any observer's causal patch. 
Since ``whether there exists a causal patch to fit'' is a highly nonlocal condition, it is effectively a break-down of local QFT.} 
modifies the last statement.
Unfortunately, since the paradox only shows a conflict with the three statements combine, it is up to individual taste/bias to modify any one of them.

@@

The most direct way to justify the classical-background assumption is to also describe the background in quantum mechanics, and verify that the quantum interaction between the background and the quantum subsystem indeed does not entangle them. 
This is clearly difficult in practice. 
The very reason why we would like to apply the classical-background approximation is to avoid describing the far-too-complicated background by quantum mechanics. 
A consistency check which requires us to do so defeats the purpose. 
In particular, there are situations in which we in-principle do not know how to describe the classical background in quantum mechanics. 
Our problem at hand, QFT in curved spacetime, is exactly such annoying situation. 
Since the classical background is the geometry, one in-principle needs to know quantum gravity in order to model the quantum interaction with the background.

Fortunately, Feynman, in his famous lectures, presented an interesting trick to circumvent the above obstacle. 
This trick, to a certain extend, enables us to perform a {\bf self-consistency check} of the classical-background assumption {\bf without} knowing the quantum nature of the background.
In Sec.\ref{sec-DoubleSlit}, we will review Feynman's analysis on the double-slit experiment. 
In his case, the double-slit is the classical background, the particle passing through it is the quantum subsystem, and subsystem unitarity is checked by whether an interference pattern can be observed on the final projection screen. 
He showed that we can ignore the quantum details of the double-slit and summarize that as an uncertainty in its position, which is a classical quantity. 
When such uncertainty is fixed, a classical calculation can show that the interference pattern is always visible as long as we put the final projection screen to be infinitely far away. 
It is in this sense that a unitary evolution of the subsystem is an arbitrarily good approximation.

@@

In Sec.\ref{sec-BlackHole}, we will provide our detail analysis and analogy. 
The classical geometry plays the role of the double-slit, a background that can potentially entangle with the Hawking quanta wavefunction and ruins its subsystem unitarity. 
We then assume that the unknown quantum nature of geometry can be parametrize by a classical uncertainty with an unknown but fixed, gauge-invariant size. 
A classical wave plays the role of the interference pattern. 
When even a classical wave decoheres due to the uncertainty of geometry, there is no reason to believed that the quantized version of such wave has unitarity.
The common expectation is that in the limit of a large black hole, gravitational effect outside the horizon is arbitrarily weak, thus local QFT should be arbitrarily trustworthy.
By analogy to Feynman's analysis, we should expect that with a fixed uncertainty in the geometry, any effect on the classical wave should drop to zero when we take the large black hole limit.
Interestingly, what we found seems to be the opposite. 
We show that with a fixed geometric uncertainty, a classical wave suffers an {\it arbitrarily large} correction in the large black hole limit.
By analogy to Feynman's analysis, this is a strong evidence that the apparent unitarity of QFT in this case is not a valid assumption.

In Sec.\ref{sec-dis}, we discuss various implications of our finding. 
First of all, our self-consistency check should be generally applicable to any geometry, and it does not invalidate local QFT entirely. 
Likewise, even when unitarity is lost in local QFT, the values of many observables do not have to change. 
Most existing applications of QFT in curved spacetime actually only care about the expectation value of particle numbers, which can be unaffected by the loss of subsystem unitarity. 
Secondly, our finding resolve the information paradox by selecting one culprit among the three statements, but it does not yet resolve the information transfer puzzle. 
We argue that our finding naturally implies an information exchange between a QFT quantum and the local geometry \cite{OsuPag16}.
The the reason why local geometry carries the appropriate information to give in the first place may be related to the soft-hair proposal \cite{HawPer16}.

@@

Double-slit interference is the signature experiment to demonstrate the nature of quantum mechanics. Figure 1 shows a simple example of such experiment.
When a group of particles of the same momentum pass through slit 1 only, they reach the final screen as some probability distribution $P_1(y)$. 
When they pass through slit 2 only, they reach the final screen as a probability distribution $P_2(y)$.
When both slits are open, the probability distribution we find on the final screen is not a simple sum; $P_{12}(y) \neq P_1(y) + P_2(y)$! 
Instead, the final screen shows an interference pattern which can only be explained by wavefunctions.
$P_i = \langle \phi_i | \phi_i \rangle$ and $P_{12} = (\langle \phi_1|+\langle \phi_2| ) (|\phi_1\rangle + | \phi_2 \rangle)=P_1 + P_2 + 2{\rm Re}\langle\phi_1|\phi_2\rangle$.

\ \\ \ \\
{\bf XXX insert the double-slit figure here: Darsh.}
\ \\ \ \\

@@

The double-slit interference is an example that both the classical coherence and quantum unitarity can be calculated explicitly and show that they follow the same condition.
Here, we advocate that such relation is actually a general rule.
{\it Classical coherence, instead of thinking it as a practically of measurements, should be treated as a prerequisit to quantum unitarity.} 
Thus when classical coherence fails, not only have we no practical measurements to confirm the purely of the subsystem wavefunction, such wavefunction {\it actually did not evolve unitarily.}
Whatever effect responsible for a classsical uncertainty large enough to disrupt classical coherence must have also interacted with the subsystem quantum-mechanically and became entangled with it.

For quantum field theory in a curved spacetime, we always assume that the quantum fields is a subsystem that never entangles with the geometry, thus remains unitary.
Since we do not know quantum gravity/geometry, we cannot directly check this assumption by an actual calculation of entanglement.
However, we can always check classical coherence, and by this rule we advocate, the answer directly prove/disprove subsystem unitarity.

If we go back to the basic of quantum field theory, this new rule we advocate makes a lot of sense. As shown in Fig.\ref{fig-QFT}, QFT starts from solving a classical mode function, then quantizing its amplitude into a quantum state. 
Any method to measure such quantum state assumes the knowledge of the classical mode function. 
If the geometric uncertainty leads to an order one change in the classical mode function, then there is no practical way to reliably measure its quantum state. 
We advocate that this is not only a practicality about measuring the quantum state, but it directly tells us that the quantum state loses its unitarity. 
Just like in Feynman's example where the uncertainty of the double-slit guarantees its entanglement with the particles, whatever effect that leads to the geometric uncertainty here must entangle with the quantum state of this mode. 
Without a theory of quantum geometry, we cannot describe how that happens. 
But through a classical calculation, we can determine whether it has happened or not.

\ \\ \ \\
{\bf XXX insert the QFT figure here: Darsh or I-Sheng}

@@

\begin{itemize}
\item {\bf Classical coherence by tracking geodesics.} The classical mode of a massless field basically has its peaks and nodes following null geodesics.
Thus, instead of actually solving the mode function, we can perform a much simpler calculation to track geodesics.
We start with two out-going null geodesics with the separation of one period of such mode near the horizon, and then we calculate the change in their separations at spatial infinity.
If such change is comparable to the wavelength, then the mode function of this wavelength loses classical coherence.
\item {\bf The background and the uncertainty.} The classical background in this case is the Schwarzschild geometry, which can be written as the metric $g_{\mu\nu}$. 
A classical uncertainty can be expressed as deviation from such metric, $\Delta g_{\mu\nu}$. 
There are two major challenges here.
\begin{enumerate}
\item There are many more variables than the double-slit experiment. 
We consider only one particular form of $\Delta g_{\mu\nu}$ in this paper---back-reactions from the presence of extra matter of zero total energy. 
It is simple to calculate and reflects the physcial intuition of vacuum pair fluctuation.
\item The value of $\Delta g_{\mu\nu}$ is gauge dependent. 
By relating it to the presence of extra matter, we can express it to a gauge-invariant local quantity, which is the natural thing to hold fixed in our analysis.
\end{enumerate}
Note that if we were reporting a positive result, that such uncertainty upholds unitarity, then one should question the validaty of learning a general lesson from a special example. However, we will show that this particular form of $\Delta g_{\mu\nu}$ is already sufficient to question unitarity, and we did not choose this form to specifically do that. Thus our limited analysis is sufficient to raise a reasonable doubt to the classical-background approximation.
\item {\bf Renormalization.} It is well-known that na\"ive applications of QFT often suffer from UV/IR divergences.
In our case, we will see that even in Minkowski space, geometric uncertainty already leads to a finite change between the two null geodesics.
We will simply ``renormalize'' that away by saying that if the black hole case leads to a similar change, it should not be taken as a serious problem.
Our surprising result is that in the black hole case, we get an infinitely larger change, which is difficult to blame on renormalization.
\end{itemize}

More concretely, our setup is like in Fig.\ref{fig-setup}. 
We start by choosing two points at some $r_0\gg M$ with a $\delta t_0\sim M$ coordinate time separation between them.
This represents one wavelength of the mode function of an asymptotic Hawking quantum.
We then back-track two null geodesics from these two points back to two points near the horizon, at $r_A$ with $(r_A-2M)\ll 2M$.
Now their separation represents one wavelength of a near-horizon mode, which would have propagated to the asymptotic mode if there were no geometric uncertainty. 
We then introduce introduce a geometric uncertainty as two shells of zero total ADM mass. 
Therefore, both the near horizon and the asymptotic regions are not affected by such uncertainty.
Only the process of propagation is affected.
With the same two starting points near the horizon. we calculate the separation $\bar{\delta t_0}$ of the two null geodesics when they arrive at $r_0$, and compare it with $\delta t_0$.

@@

As the first step, we set $M=0$ in Eq.~(\ref{eq-result}) to study its meaning in Minkowski space. Assuming that $|r_1-r_2| \equiv \Delta r \ll r_1$ and $\Delta M \ll r_1$, the leading order result becomes
\begin{equation}
\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} \approx \frac{\Delta M}{r_1^2} \Delta r 
\equiv \sigma \Delta r~.
\label{eq-Mink}
\end{equation}
This seems to be a reasonable answer. 
First of all, it is quite unlikely that the entire shell of mass $\Delta M$ fluctuates out of vacuum.
It is reasonable that any change to the null geodesics is about a local energy density of the particular piece of shell they happen to pass through.
Secondly, this result is gauge invariant. For an observer at rest, $\sigma$ is the local energy density and $\Delta r$ is the proper distance. 
For a boosted observer, $\sigma$ increases by a boost factor while $\Delta r$ contracts by the same factor.
We take it as a good sign that other forms of geometric uncertainty can also be parametrize by a similar, gauge invariant quantity.

@@

Next we study Eq.~(\ref{eq-result}) with an actual black hole. 
When the double-shell is very far away from the black hole, $r_1\gg M$, it agrees with Eq.~(\ref{eq-Mink}) as expected. 
The interesting thing here is that when this pair of geodesics originate near the horizon, the double-shell could also be somewhere near the horizon. 
In that limit, Eq.~(\ref{eq-result}) can be approximated by
\begin{equation}
\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} \approx
\sigma \Delta l \left(\frac{2M}{l_1}\right)^2~, \ \ \ \ {\rm \bf XXX \ check \ coefficients}
\label{eq-NearHorizon}
\end{equation}
where $l$ is the proper distance between $r_1$ and the horizon and $\Delta l$ is the proper distance between the two shells. 
We can see that in addition to the same gauge-invariant quantity in Minkowski space
\footnote{In Minkowski space, the radial coordinate is the proper distance, $\Delta r=\Delta l$.}, 
there is an extra factor of $(2M/l_1)^2$ which diverges as the shell approaches the horizon.

The small $l_1$ limit may not be the best way to appreciate how Eq.~(\ref{eq-NearHorizon}) poses a threat to QFT. 
After all, we do not expect QFT to hold for arbitrarily small distance anyway. 
The best way to understand Eq.~(\ref{eq-NearHorizon}) is to fix $l_1$ at some scale that much longer than any scale that we expect UV problems. 
By conventional knowledge, the effect of gravity near horizon gets arbitrarily weak as the black hole becomes large. 
However, the problem caused by Eq.~(\ref{eq-NearHorizon}) grows larger as the black hole becomes larger, and diverges in the large black hole limit.
Since the large black hole limit is supposed to be the best case scenario for information paradox, such a diverging uncertainty to decohere classical waves causes a strong doubt on the subsystem unitarity assumption in QFT.

\section{Discussion}

@@

In this paper, we proposed a self-consistency check of local QFT in curved spacetime geometries.
We have shown that the near-horizon geometry of a Schwarzschild black hole seems to fail such check.
As explained in Sec.\ref{sec-BlackHole}, the consistency requires us to parametrize the uncertainty in the classical geometry.
We have chosen a particular form of uncertainty in our explicit calculation.
Our result is gauge invariant and makes physical sense, but there might be a more general way to parametrize such uncertainty to make our approach even more general.
It is also interesting to apply the same check to other geometries, especially other types of horizons.

@@

Showing the lack of unitarity in the propagation of Hawking quanta does not resolve all the problem. 
Usually, one pictures a nonunitarity process as losing information. 
In the context of black hole information, a Hawking quantum actually has to {\it recover} information. 
A near-horizon mode starts from a maximally mixed (thermal) state with no information, since its partner is the interior mode that never comes out of the horizon. 
After the nonunitarity propagation to become an asymptotic Hawking quantum, it has to carry information to purify the rest of the Hawking radiation there.

@@

\subsection{Proper time}

\subsubsection{Background spacetime}

First we consider the motion of Hawking photons coming from a Schwarzschild metric of the form

\begin{equation}
	ds^2 = - \left( 1 - \frac{2M}{r} \right) dt^2 + \left( 1 - \frac{2M}{r} \right)^{-1} dr^2 + r^2 d \Omega_2^2.
\end{equation}

Consider two Hawking photons coming from a fixed distance, $r_{e}$, just above a Schwarzschild black hole separated by a coordinate time interval $\bar{\delta t}_A$ and a corresponding proper time $\bar{\delta \tau}_A$ as shown in figure \ref{fig:1}. The two photons propagate through to the observer at $r_0$ following geodesics. We could potentially solve for the geodesics of the photons to find out the coordinate time of arrival of each photon, however in the absence of additional gravitational fields the coordinate time interval between the photons will not change\footnote{This will prove to be extremely helpful when we look at the calculation in the presence of shells.}, i.e $\bar{\delta t}_A = \bar{\delta t}_0$, and that is the quantity we need in order to compute the proper time $\bar{\delta \tau}_0$ observed by the observer at $r_0$,

\begin{eqnarray}
	\bar{\delta \tau}_0 & = & \left( 1- \frac{2M}{r_0} \right)^\frac{1}{2} \bar{\delta t}_0	\nonumber	\\
	& = & \left( 1 - \frac{2M}{r_0} \right)^\frac{1}{2} \bar{\delta t}_A \approx \bar{\delta t}_{A} 
\end{eqnarray}

where in the last step we have assumed $r_0$ is very large.

\subsubsection{Introducing perturbations: Double shells}

\begin{figure}[h!]
\begin{center}
\includegraphics[scale = 0.6]{Propertime.pdf}
\caption{The two parts of this diagrams describe two different scenarios. The trajectories of the photon are the lines in orange. The trajectory of the observer and the position from which the photons are emitted are represented by solid blue lines. The bottom part is a general case of two Hawking photons coming from a distance $r_A$ from the black hole of mass $M$ and arriving at an observer who is at a distance of $r_0$. The top part shows two Hawking photons coming from the same distance $r_A$ from a black hole of mass $M$. Instead of the photons freely propagating through to an observer at $r_0$, they have to cross two shells, represented by blue dotted line, of equal and opposite mass $-\Delta M, \Delta M$ at $r_{1}, r_{2}$ respectively. The regions $I$ represent a metric with mass $M$ and region $II$ represents a metric with mass $M-\Delta M$.}
\label{fig:1}
\end{center}
\end{figure}

>>>>

\begin{abstract}
The black hole information paradox presumes that local quantum field theory can provide unitary propagations for near-horizon modes to asymptotic Hawking quanta. 
Instead of invoking unknown quantum-gravity effects to modify this assumption, we propose a self-consistency check.
We re-examine this assumption by establishing an analogy to Feynman's analysis of a double-slit experiment. 
Feynman showed that the assumption of subsystem unitarity in double-slit experiment, namely ignoring the entanglement with the double-slit, becomes arbitrarily reliable when the screen to project the interference pattern on goes infinitely far away.
Analogously, here we ask whether unitary propagation of Hawking quanta, namely ignoring the entanglement with the geometry, also becomes arbitrarily reliable in the limit of a large black hole. 
We present strong evidence that the result is negative, and we discuss how this is related to the information transfer from near-horizon geometry and the soft-hair proposal.
\end{abstract}

@@

This conflict has inspired many different proposals to modify one of the above three statements. 
For example, information loss or remnant \cite{Bek94} {\bf (XXX anyone knows a better reference for remnants?)} modifies the first statement; 
firewall \cite{BraPir09,AMPS} or ER=EPR \cite{MalSus13} modifies the second statement;
various proposals of nonlocal effects near the horizon \cite{Gid12,DodSil15,OsuPag16} or causal patch complementarity \cite{HuiYan13,IlgYan13,LowTho14}
\footnote{Independent of the particular realization, causal-patch complementarity basically claims that QFT breaks down if one applies it to a region that does not fit into any observer's causal patch. 
Since ``whether there exists a causal patch to fit'' is a highly nonlocal condition, it is effectively a break-down of local QFT.} 
modifies the last statement.
Unfortunately, since the paradox only shows a conflict with the three statements combined, it is up to individual taste/bias to modify any one of them.

@@

The most direct way to justify the classical-background assumption is to also describe the background in quantum mechanics, and verify that the quantum interaction between the background and the quantum subsystem indeed does not entangle them. 
This is clearly difficult in practice. 
The very reason why we would like to apply the classical-background approximation is to avoid describing the far-too-complicated background by quantum mechanics. 
A consistency check which requires us to do so defeats the purpose. 
In particular, there are situations in which we in-principle do not know how to describe the classical background in quantum mechanics. 
Our problem at hand, QFT in curved spacetime, is exactly this annoying situation. 
Since the classical background is the geometry, one in-principle needs to know quantum gravity in order to model the quantum interaction with the background.

Fortunately, Feynman, in his famous lectures, presented an interesting trick to circumvent this obstacle. 
This trick, to a certain extend, enables us to perform a {\bf self-consistency check} of the classical-background assumption {\bf without} knowing the quantum nature of the background.
In Sec.\ref{sec-DoubleSlit}, we will review Feynman's analysis of the double-slit experiment. 
In his case, the double-slit is the classical background, the particle passing through it is the quantum subsystem, and subsystem unitarity is checked by whether an interference pattern can be observed on the final projection screen. 
He showed that we can ignore the quantum details of the double-slit and summarize that as an uncertainty in its position, which is a classical quantity. 
When such uncertainty is fixed, a classical calculation can show that the interference pattern is always visible as long as we put the final projection screen to be infinitely far away. 
It is in this sense that a unitary evolution of the subsystem is an arbitrarily good approximation.

@@

In Sec.\ref{sec-BlackHole}, we will provide our detailed analysis and analogy. 
The classical geometry plays the role of the double-slit, a background that can potentially entangle with the Hawking quanta wavefunction and ruin its subsystem unitarity. 
We then assume that the unknown quantum nature of geometry can be parametrized by a classical uncertainty with an unknown but fixed, gauge-invariant size. 
A classical wave plays the role of the interference pattern. 
When even a classical wave decoheres due to the uncertainty of geometry, there is no reason to believed that the quantized version of such wave has unitarity.
The common expectation is that in the limit of a large black hole, gravitational effects outside the horizon are arbitrarily weak, thus local QFT should be arbitrarily trustworthy.
By analogy to Feynman's analysis, we should expect that with a fixed uncertainty in the geometry, any effect on the classical wave should drop to zero when we take the large black hole limit.
Interestingly, what we found seems to be the opposite. 
We show that with a fixed geometric uncertainty, a classical wave suffers an {\it arbitrarily large} correction in the large black hole limit.
By analogy to Feynman's analysis, this is a strong evidence that the apparent unitarity of QFT in this case is not a valid assumption.

In Sec.\ref{sec-dis}, we discuss various implications of our finding. 
First of all, our self-consistency check should be generally applicable to any geometry, and it does not invalidate local QFT entirely. 
Likewise, even when unitarity is lost in local QFT, the values of many observables do not have to change. 
Most existing applications of QFT in curved spacetime actually only care about the expectation value of particle numbers, which can be unaffected by the loss of subsystem unitarity. 
Secondly, our finding resolves the information paradox by selecting one culprit among the three statements, but it does not yet resolve the information transfer puzzle. 
We argue that our finding naturally implies an information exchange between a QFT quantum and the local geometry \cite{OsuPag16}.
The reason why local geometry carries the appropriate information to give in the first place may be related to the soft-hair proposal \cite{HawPer16}.

@@

Double-slit interference is the signature experiment to demonstrate the nature of quantum mechanics. Figure 1 shows a simple example of such experiment.
When a group of particles of the same momentum pass through slit 1 only, they reach the final screen as some probability distribution $P_1(y)$. 
When they pass through slit 2 only, they reach the final screen as a probability distribution $P_2(y)$.
When both slits are open, the probability distribution we find on the final screen is not a simple sum; $P_{12}(y) \neq P_1(y) + P_2(y)$
Instead, the final screen shows an interference pattern which can only be explained by wavefunctions.
$P_i = \langle \phi_i | \phi_i \rangle$ and $P_{12} = (\langle \phi_1|+\langle \phi_2| ) (|\phi_1\rangle + | \phi_2 \rangle)=P_1 + P_2 + 2{\rm Re}\langle\phi_1|\phi_2\rangle$.

\begin{figure}[h!]
\begin{center}.
\includegraphics[scale = 0.5]{DSe.pdf}
\caption{Schematic of the double slit experiment. The diagram shows two different scenarios. The top figure shows the behaviour one would expect of classical particles going through one slit or the other. The bottom figure shows the behaviour of classical waves creating an interference patter. Screen one shows the signal that one would see in each scenario (i.e classical particles or waves) if only one slit was open. If slit 1 was open we would see $P_1$ and see on. Screen 2 shows the signal we see if both the silts are open in each scenario.}
\label{fig-doubleslit}
\end{center}
\end{figure}

@@

The double-slit interference is an example that both the classical coherence and quantum unitarity can be calculated explicitly and show that they follow the same condition.
Here, we advocate that such a relation is actually a general rule.
{\it Classical coherence, instead of thinking of it as a practicality of measurements, should be treated as a prerequisit to quantum unitarity.} 
Thus when classical coherence fails, not only have we no practical measurements to confirm the purity of the subsystem wavefunction, such wavefunctions {\it actually did not evolve unitarily.}
Whatever effect responsible for a classical uncertainty large enough to disrupt classical coherence must have also interacted with the subsystem quantum-mechanically and became entangled with it.

For quantum field theory in a curved spacetime, we always assume that the quantum field is a subsystem that never entangles with the geometry, thus remains unitary.
Since we do not know quantum gravity/geometry, we cannot directly check this assumption by an actual calculation of entanglement.
However, we can always check classical coherence, and by this rule we advocate, the answer directly proves/disproves subsystem unitarity.

If we go back to the basics of quantum field theory, this new rule we advocate makes a lot of sense. As shown in Fig.\ref{fig-QFT}, QFT starts from solving a classical mode function $|\psi \rangle$, then quantizing its amplitude into a quantum state. 
Any method to measure such quantum state assumes the knowledge of the classical mode function. 
If the geometric uncertainty leads to an order one change in the classical mode function, then there is no practical way to reliably measure its quantum state. 
We advocate that this is not only a practicality about measuring the quantum state, but it directly tells us that the quantum state loses its unitarity. 
Just like in Feynman's example where the uncertainty of the double-slit guarantees its entanglement with the particles, whatever effect that leads to the geometric uncertainty here must entangle with the quantum state of this mode. 
Without a theory of quantum geometry, we cannot describe how that happens. 
But through a classical calculation, we can determine whether it has happened or not.

\begin{figure}[h!]
\begin{center}.
\includegraphics[scale = 0.5]{bh_coherence.pdf}
\caption{Schematic showing the rule we advocate; as classical coherence fails, we loose quantum unitarity.}
\label{fig-QFT}
\end{center}
\end{figure}

@@

\begin{itemize}
\item {\bf Classical coherence by tracking geodesics.} The classical mode of a massless field basically has its peaks and nodes following null geodesics.
Thus, instead of actually solving the mode function, we can perform a much simpler calculation to track geodesics.
We start with two out-going null geodesics with the separation of one period of such mode near the horizon, and then we calculate the change in their separations at spatial infinity.
If this change is comparable to the wavelength, then the mode function of this wavelength loses classical coherence.
\item {\bf The background and the uncertainty.} The classical background in this case is the Schwarzschild geometry, which can be written as the metric $g_{\mu\nu}$. 
A classical uncertainty can be expressed as deviation from such metric, $\Delta g_{\mu\nu}$. 
There are two major challenges here.
\begin{enumerate}
\item There are many more variables than the double-slit experiment. 
We consider only one particular form of $\Delta g_{\mu\nu}$ in this paper---back-reactions from the presence of extra matter of zero total energy. 
It is simple to calculate and reflects the physcial intuition of vacuum pair fluctuation.
\item The value of $\Delta g_{\mu\nu}$ is gauge dependent. 
By relating it to the presence of extra matter, we can express it to a gauge-invariant local quantity, which is the natural thing to hold fixed in our analysis.
\end{enumerate}
Note that if we were reporting a positive result, that such uncertainty upholds unitarity, then one should question the validaty of learning a general lesson from a special example. However, we will show that this particular form of $\Delta g_{\mu\nu}$ is already sufficient to question unitarity, and we did not choose this form to specifically do that. Thus our limited analysis is sufficient to raise a reasonable doubt to the classical-background approximation.
\item {\bf Renormalization.} It is well-known that na\"ive applications of QFT often suffer from UV/IR divergences.
In our case, we will see that even in Minkowski space, geometric uncertainty already leads to a finite change between the two null geodesics.
We will simply ``renormalize'' that away by saying that if the black hole case leads to a similar change, it should not be taken as a serious problem.
Our surprising result is that in the black hole case, we get an infinitely larger change, which is difficult to blame on renormalization.
\end{itemize}

More concretely, our setup is shown in Fig.\ref{fig-setup}. 
We start by choosing two points at some $r_0\gg M$ with a $\delta t_0\sim M$ coordinate time separation between them.
This represents one wavelength of the mode function of an asymptotic Hawking quantum.
We then back-track two null geodesics from these two points back to two points near the horizon, at $r_A$ with $(r_A-2M)\ll 2M$.
Now their separation represents one wavelength of a near-horizon mode, which would have propagated to the asymptotic mode if there were no geometric uncertainty. 
We then introduce introduce a geometric uncertainty as two shells of zero total ADM mass. 
Therefore, both the near horizon and the asymptotic regions are not affected by such uncertainty.
Only the process of propagation is affected.
With the same two starting points near the horizon. we calculate the separation $\bar{\delta t_0}$ of the two null geodesics when they arrive at $r_0$, and compare it with $\delta t_0$.

@@

As the first step, we set $M=0$ in Eq.~(\ref{eq-result}) to study its meaning in Minkowski space. Assuming that $|r_1-r_2| \equiv \Delta r \ll r_1$ and $\Delta M \ll r_1$, the leading order result becomes
\begin{equation}
\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} \approx - \frac{\Delta M}{r_1^2} \Delta r 
\equiv \sigma \Delta r~.
\label{eq-Mink}
\end{equation}
This seems to be a reasonable answer. 
First of all, it is quite unlikely that the entire shell of mass $\Delta M$ fluctuates out of vacuum.
It is reasonable that any change to the null geodesics is about a local energy density of the particular piece of shell they happen to pass through.
Secondly, this result is gauge invariant. For an observer at rest, $\sigma$ is the local energy density and $\Delta r$ is the proper distance. 
For a boosted observer, $\sigma$ increases by a boost factor while $\Delta r$ contracts by the same factor.
We take it as a good sign that other forms of geometric uncertainty can also be parametrize by a similar, gauge invariant quantity.

@@

Next we study Eq.~(\ref{eq-result}) with an actual black hole. 
When the double-shell is very far away from the black hole, $r_1\gg M$, it agrees with Eq.~(\ref{eq-Mink}) as expected. 
The interesting thing here is that when this pair of geodesics originate near the horizon, the double-shell could also be somewhere near the horizon. 
In that limit, Eq.~(\ref{eq-result}) can be approximated by
\begin{equation}
\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} \approx
- \sigma \Delta l \left(\frac{2M}{l}\right)^2~, \ \ \ \ {\rm \bf XXX \ check \ coefficients}
\label{eq-NearHorizon}
\end{equation}
where $l$ is the proper distance between $r_1$ and the horizon and $\Delta l$ is the proper distance between the two shells. 
We can see that in addition to the same gauge-invariant quantity in Minkowski space
\footnote{In Minkowski space, the radial coordinate is the proper distance, $\Delta r=\Delta l$.}, 
there is an extra factor of $(2M/l)^2$ which diverges as the shell approaches the horizon.

The small $l$ limit may not be the best way to appreciate how Eq.~(\ref{eq-NearHorizon}) poses a threat to QFT. 
After all, we do not expect QFT to hold for arbitrarily small distance anyway. 
The best way to understand Eq.~(\ref{eq-NearHorizon}) is to fix $l$ at some scale that much longer than any scale that we expect UV problems. 
By conventional knowledge, the effect of gravity near horizon gets arbitrarily weak as the black hole becomes large. 
However, the problem caused by Eq.~(\ref{eq-NearHorizon}) grows larger as the black hole becomes larger, and diverges in the large black hole limit.
Since the large black hole limit is supposed to be the best case scenario for information paradox, such a diverging uncertainty to decohere classical waves causes a strong doubt on the subsystem unitarity assumption in QFT.

\section{Discussion}
\label{sec-dis}

@@

In this paper, we proposed a self-consistency check of local QFT in curved spacetime geometries.
We have shown that the near-horizon geometry of a Schwarzschild black hole seems to fail such a check.
As explained in Sec.\ref{sec-BlackHole}, the consistency requires us to parametrize the uncertainty in the classical geometry.
We have chosen a particular form of uncertainty in our explicit calculation.
Our result is gauge invariant and makes physical sense, but there might be a more general way to parametrize such uncertainty to make our approach even more general.
It is also interesting to apply the same check to other geometries, especially other types of horizons.

@@

Showing the lack of unitarity in the propagation of Hawking quanta does not resolve all the problems. 
Usually, one pictures a nonunitarity process as losing information. 
In the context of black hole information, a Hawking quantum actually has to {\it recover} information. 
A near-horizon mode starts from a maximally mixed (thermal) state with no information, since its partner is the interior mode that never comes out of the horizon. 
After the nonunitarity propagation to become an asymptotic Hawking quantum, it has to carry information to purify the rest of the Hawking radiation there.

@@

A black hole of mass $M$ defines a Schwarzschild geometry for the spacetime with the following metric

\begin{equation}
	ds^2 = - \left( 1 -\frac{2M}{r} \right) dt^2 + \left( 1 - \frac{2M}{r} \right)^{-1} dr^2 + r^2 d \Omega_2^2	\label{1}
\end{equation}

where we are working with units in which $G = c = 1$. We know there will be a flux of particles appearing from the horizon of the black hole \cite{Haw74}. Take some coordinate time interval, $\delta \bar{t_e}$, (which will have some corresponding proper time interval $\delta \bar{\tau_e}$) between two consecutive particles being emitted from the same position above the horizon of the black hole. An observer far away will see these particles arrive with some coordinate time interval $\delta \bar{t_0}$. We can follow the trajectory of the particles (assuming they are relativistic) from the position they are emitted, $r_e$, to the observer at $r_0$ by setting $ds = 0$ in Eq (\ref{1}). By confining the motion to be only in the radial direction, i.e $d \Omega_2 = 0$, we get the following geodesic equation

\begin{equation}
	\bar{t_e}^{(1)} - \bar{t_0}^{(1)} = \bar{r_0} - \bar{r_e} + 2M \ln \left( \frac{\bar{r_0} - 2M}{\bar{r_e} - 2M}  \right)	\label{3}
\end{equation}

where the superscript represents particle $1$ so $\bar{t_e}^{(1)}$ represents the time at which particle $1$ is emitted, $\bar{t_0}^{(1)}$ is when particle 1 is observed. Analogously for a particle $2$ that is emitted at $\bar{t_e}^{(2)}$ we have

\begin{equation}
	\bar{t_e}^{(2)} - \bar{t_0}^{(2)} = \bar{r_0} - \bar{r_e} + 2M \ln \left( \frac{\bar{r_0} - 2M}{\bar{r_e} - 2M}  \right).	\label{4}
\end{equation}

Since the right hand side of Eq (\ref{3}) and (\ref{4}) is the same, we see that

\begin{equation}
	\bar{t_0}^{(2)} - \bar{t_0}^{(1)} = \bar{t_e}^{(2)} - \bar{t_e}^{(1)} \Rightarrow \delta \bar{t_0} = \delta \bar{t_e}.
\end{equation}

Therefore the coordinate time interval when the particles are emitted remains the same when it is observed at distance $r_0$ as is shown in the bottom part of figure \ref{fig-setup}.

We can convert $\delta\bar{t_0}$ to proper time

\begin{equation}
	\delta \bar{\tau_0} = \left( 1 -\frac{2M}{r_0} \right)^\frac{1}{2} \delta \bar{t_0}
\end{equation}

and in the limit that the observer is very far away $\delta \bar{\tau_0} \approx \delta \bar{t_0}$.

\subsubsection{Perturbed spacetime - double shell}

Now we introduce two shells of matter with equal and opposite ADM mass, $-\Delta M$ and $\Delta M$ where $|\Delta M|<<M$, at a distance of $r_1$ and $r_2$ respectively as shown in the top part of figure \ref{fig-setup}. We model these shells as infinitesimally thin and therefore use the Israel Junction Conditions (IJC) \cite{Isr66} with a delta function shell to analyze the effects of the shells. In this case the particle's move through two different spacetime regions. Region $I$ is defined by the black hole of mass $M$ and region $II$ is defined by a Schwarzschild metric of mass $M-\Delta M$ as shown in the top part of figure \ref{fig-setup}.
\\
\\
As explained in the previous section, the proper time interval between two particles emitted at $r_e$, $\delta t_e$, is the same as the coordinate time interval at $r_1$, $\delta t_1$. Now we need to find the corresponding coordinate time interval in region $II$, $\delta \hat{t}_1$ (in general we will use hats on top of quantities that are evaluated in region $II$). To do this we simply note that the corresponding proper time at $r_1$, $\delta \tau_1$ must be the same in both regions of spacetime - this is a simple consequence of the IJC. The coordinate time intervals at $r_1$, in the two different regions, are therefore related by
